---
title: 'Lab 3: QTW'
author: "Sean Kennedy"
date: "6/11/2020"
output: pdf_document
---

```{r setup, include=FALSE}
library(reticulate)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
knitr::knit_engines$set(python = eng_python)
use_python('/usr/local/bin/python3')
```

```{r}
load('./Data/data.Rda')
```

```{python}
from sklearn.model_selection import train_test_split
from sklearn.tree import DecisionTreeClassifier, export_graphviz
from sklearn import tree
from sklearn.metrics import accuracy_score

# Recommended Installation: 'conda install python-graphviz' (should add 'graphviz' to PATH)
from graphviz import Source
import pandas as pd

import seaborn as sns
```

### Data Dictionary

```{python DATA_CLEANUP}
df = r.emailDFrp
df.info()
```

```{python}
df.describe()

```

```{python}
df.columns[df.isna().any() == True]
```


```{python}
df.subSpamWords.unique()
```

This is just a boolean parameter, let's check the frequency distribution.

```{python}
spam_na = df[df.subSpamWords.isna()]
group_by_spam = df.groupby(['subSpamWords', 'isSpam']).count().reset_index().rename(columns={'isRe':'Count'})
p1 = sns.barplot(data = group_by_spam, x='subSpamWords', y='Count', hue='isSpam')
p1.set_title('Sub Spam Words vs Is Spam')
p1.set_yticklabels([f'{y:,.0f}' for y in p1.get_yticks()])
p1

```

```{python}
group_by_spam.groupby(['subSpamWords', 'isSpam'])['Count'].sum()

```


```{python}
p2 = sns.barplot(data = spam_na.groupby(['isSpam']).count().reset_index().rename(columns={'isRe':'Count'}), x='isSpam', y='Count')
p2.set_title('subSpamWords == N/A vs isSpam')
y_ticklabels = [f'{y:,.0f}' for y in p2.get_yticks()]
p2.set_yticklabels(y_ticklabels)
p2
```

```{python}
spam_na.groupby(['isSpam'])['isRe'].count()

```

From the above, we can see that the ratio of non-spam emails vs. spam emails is higher when **subSpamWords** is False It is the opposite for the case where **subSpamWords** is True. Since each of these emails have been classified as not spam, we can safely assume that these are most likely should be imputed to our **False** class for **subSpamWords**. There are 7 observations for this particular field being N/A, so the effect overall of any imputation is likely minimal, at best.


***noHost***

```{python}
df.noHost.unique()
```

Again, this is just a boolean parameter, let's check the frequency distribution.


```{python}
host_na = df[df.noHost.isna()]
group_by_host = df.groupby(['noHost', 'isSpam']).count().reset_index().rename(columns={'isRe':'Count'})
p1 = sns.barplot(data = group_by_host, x='noHost', y='Count', hue='isSpam')
p1.set_title('No Host vs Is Spam')
p1.set_yticklabels([f'{y:,.0f}' for y in p1.get_yticks()])
p1

```

```{python}
group_by_host.groupby(['noHost', 'isSpam'])['Count'].sum()

```

```{python}
p2 = sns.barplot(data = host_na.groupby(['isSpam']).count().reset_index().rename(columns={'isRe':'Count'}), x='isSpam', y='Count')
p2.set_title('noHost == N/A vs isSpam')
y_ticklabels = [f'{y:,.0f}' for y in p2.get_yticks()]
p2.set_yticklabels(y_ticklabels)
p2
```

```{python}
host_na.groupby(['isSpam'])['isRe'].count()
```

In this case, the **noHost** field only has one N/A, so its impact is negligable - given the observed distribution of this field (strongly tilted towards the **True** class) - it's highly unlikely that this field would e false to begin with, regardless of its classification as spam or not. Hence, we'll impute this value to **True**. 

***isYelling***

```{python}
yelling_na = df[df.isYelling.isna()]
group_by_yelling = df.groupby(['isYelling', 'isSpam']).count().reset_index().rename(columns={'isRe':'Count'})
p1 = sns.barplot(data = group_by_yelling, x='isYelling', y='Count', hue='isSpam')
p1.set_title('Is Yelling vs Is Spam')
p1.set_yticklabels([f'{y:,.0f}' for y in p1.get_yticks()])
p1

```

```{python}
group_by_yelling.groupby(['isYelling', 'isSpam'])['Count'].sum()

```


```{python}
p2 = sns.barplot(data = yelling_na.groupby(['isSpam']).count().reset_index().rename(columns={'isRe':'Count'}), x='isSpam', y='Count')
p2.set_title('isYelling == N/A vs isSpam')
y_ticklabels = [f'{y:,.0f}' for y in p2.get_yticks()]
p2.set_yticklabels(y_ticklabels)
p2
```

```{python}
yelling_na.groupby(['isSpam'])['isRe'].count()
```

From the above, we can see that the ratio of non-spam emails vs. spam emails is higher when **isYelling** is False. It is the opposite for the case where **isYelling** is True, nearly all of those observations were spam emails. Since each of these emails have been classified as not spam, we can safely assume that these should be imputed to our **False** class for **isYelling**. There are 7 observations for this particular field being N/A, so the effect overall of any imputation is likely minimal, at best.

***subBlanks***


```{python}
df[df.subBlanks.isna()].groupby(['isSpam'])[['isRe']].count().rename(columns={'isRe':'Count'})
```

```{python sub_blanks_distribution}
not_na = df[~df.subBlanks.isna()]['subBlanks']
not_na.hist()

###Page 151 of text is 
```
```{python}
not_na.describe()
print(f'Median = {round(not_na.median(), 4)}')
```

```{python sub_blanks_distribution_spam}
true_na = df[(~df.subBlanks.isna())
& (df.isSpam == 'T')
]['subBlanks']
true_na.hist()
```

```{python sub_blanks_distribution_spam}
false_na = df[(~df.subBlanks.isna())
& (df.isSpam == 'F')
]['subBlanks']
false_na.hist()
```

```{python}
df.subBlanks.unique()
```

```{python sub_blanks_distribution_spam}
true_na.describe()
print(true_na.median())
```



### Data Partitioning

```{python}

df = df.dropna() # TODO: Impute NAs, don't drop them

features = df[df.columns.difference(['isSpam'])]

X = pd.get_dummies(features, drop_first=True)
y = df['isSpam']

X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=0.20, random_state=7333)

```

### Modeling - Decision Tree

```{python}

clf = DecisionTreeClassifier(random_state=7333)
clf.fit(X_train, y_train)

pred = clf.predict(X_test)

# Accuracy
accuracy_score(y_test, pred)

```


```{python}
#X_test.columns
y_test.index
```



```{python}

graph = Source(tree.export_graphviz(clf, feature_names=X.columns, class_names=['spam', 'ham'], filled = True))


```
